cardinalR: Generating interesting high-dimensional data structures

### 2025-04-26 paper-cardinalR.Rmd
Added explanation for arguments in main function

Add main function argument list to a table...

```{r, echo=TRUE, eval=FALSE}
gen_multicluster(
  n = c(200, 300, 500), p = 4, k = 3,
  loc = matrix(c(
    0, 0, 0, 0,
    5, 9, 0, 0,
    3, 4, 10, 7
  ), nrow = 4, byrow = TRUE),
  dim_weights = dim4_weights,
  scale = c(3, 1, 2),
  shape = c("gaussian", "bluntedcorn", "unifcube"),
  rotation = rotations_4d,
  is_bkg = FALSE
)
```

>>>>

```{r}
main_tb <- tibble(arg = c("n",
                            "p",
                            "k",
                            "loc",
                            "scale",
                            "shape",
                            "rotation",
                            "is_bkg"), 
                        exp = c("A numeric vector representing the sample sizes.",
                                "A numeric value representing the number of dimensions.",
                                "A numeric value representing the number of clusters.",
                                "A numeric matrix representing the locations/centroids of clusters.",
                                "A numeric vector representing the scaling factors of clusters.",
                                "A character vector representing the shapes of clusters.",
                                "A numeric list which contains plane and the corresponding angle along that plane for each cluster.",
                                "A Boolean value representing the background noise should exist or not."))
```

```{r main-tb-html, eval=knitr::is_html_output()}
main_tb |> 
  kable(caption = "The main arguments for `gen_multicluster()`.", col.names = c("Argument", "Explanation")) 
```

```{r main-tb-pdf, eval=knitr::is_latex_output()}
main_tb |> 
  kable(caption = "The main arguments for `gen_multicluster()`.", format="latex", col.names = c("Argument", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```
